### 2017-06-14 categorical-models.tex
Proof of strong monad.

\begin{definition}
  A \textbf{symmetric monoidal category} is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ together with a natural transformation with
  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called exchange, such that the
  following diagrams commute:
  \begin{mathpar}
  \bfig
    \Vtriangle<300,400>[A\otimes I`I\otimes A`A;\e{A,I}`\rho_A`\lambda_A]
  \efig
  \and
  \bfig
    \Vtriangle/=`->`<-/<300,400>[
      A\otimes B`A\otimes B`B\otimes A;
      id_{A\otimes B}`\e{A,B}`\e{B,A}]
  \efig
  \and
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (A\otimes B)\otimes C`A\otimes(B\otimes C)`(B\otimes C)\otimes A`
      (B\otimes A)\otimes C`B\otimes(A\otimes C)`B\otimes(C\otimes A);
      \alpha_{A,B,C}`\e{A,B\otimes C}`\e{A,B}\otimes id_C``
      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\otimes\e{A,C}]
  \efig
  \end{mathpar}
\end{definition}

@@

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{symmetric
  monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor $(F,m)$ that satisfies
  the following coherence diagram:
  \begin{mathpar}
  \bfig
    \square<700,400>[
      FA\otimes'FB`FB\otimes'FA`F(A\otimes B)`F(B\otimes A);
      \e{FA,FB}`\m{A,B}`\m{B,A}`F\e{A,B}]
  \efig
  \end{mathpar}
\end{definition}

@@

@@

  and $(F,m)$ and $(G,n)$ are monoidal functors. \\

@@

        $\mu=\varepsilon_{GFA}$, $\mu$ is obviously also monoidal since $\varepsilon$ also is.
        Thus the following diagrams commute.

@@

Therefore, the monad is non-commutative.

>>>>

\begin{definition}
  A \textbf{symmetric monoidal category} (SMCC) is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ together with a natural transformation with
  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called \textbf{exchange}, such that the
  following diagrams commute:
  \begin{mathpar}
  \bfig
    \Vtriangle<300,400>[A\otimes I`I\otimes A`A;\e{A,I}`\rho_A`\lambda_A]
  \efig
  \and
  \bfig
    \Vtriangle/=`->`<-/<300,400>[
      A\otimes B`A\otimes B`B\otimes A;
      id_{A\otimes B}`\e{A,B}`\e{B,A}]
  \efig
  \and
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (A\otimes B)\otimes C`A\otimes(B\otimes C)`(B\otimes C)\otimes A`
      (B\otimes A)\otimes C`B\otimes(A\otimes C)`B\otimes(C\otimes A);
      \alpha_{A,B,C}`\e{A,B\otimes C}`\e{A,B}\otimes id_C``
      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\otimes\e{A,C}]
  \efig
  \end{mathpar}
\end{definition}

@@

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{symmetric
  monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor $(F,\m{})$ that
  satisfies the following coherence diagram:
  \begin{mathpar}
  \bfig
    \square<700,400>[
      FA\otimes'FB`FB\otimes'FA`F(A\otimes B)`F(B\otimes A);
      \e{FA,FB}`\m{A,B}`\m{B,A}`F\e{A,B}]
  \efig
  \end{mathpar}
\end{definition}

@@

  \label{lem:monoidal-monad}

@@

  and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. \\

@@

        $\mu=\varepsilon_{GFA}$ and $\varepsilon$ is monoidal, so is $\mu$. Thus the following
        diagrams commute.

@@

\begin{definition}
  \label{def:strong-monad}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ be a monoidal category and $(T,\eta,\mu)$ be a
  monad on $\cat{M}$. $T$ is a \textbf{strong monad} if there is natural transformation $\tau$, 
  called the \textbf{tensorial strength}, with components
  $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ such that the following diagrams commute:
  \begin{mathpar}
  \bfig
    \Vtriangle<400,400>[I\otimes TA`T(I\otimes A)`TA;\tau_{I,A}`\lambda_{TA}`T\lambda_A]
  \efig
  \and
  \bfig
    \Vtriangle<400,400>[
      A\otimes B`A\otimes TB`T(A\otimes B);id_A\otimes\eta_B`\eta_{A\otimes B}`\tau_{A,B}]
  \efig
  \and
  \bfig
    \square/->`->`->`/<1800,400>[
      (A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`
      A\otimes(B\otimes TC)`T(A\otimes(B\otimes C));
      \tau_{A\otimes B,C}`\alpha_{A,B,TC}`T\alpha_{A,B,C}`]
    \morphism<900,0>[A\otimes(B\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\tau_{B,C}]
    \morphism(900,0)<900,0>[A\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\tau_{A,B\otimes C}]
  \efig
  \and
  \bfig
    \square/`->`->`->/<1400,400>[
      A\otimes T^2B`T^2(A\otimes B)`A\otimes TB`T(A\otimes B);
      `id_A\otimes\mu_B`\mu_{A\otimes B}`\tau_{A,B}]
    \morphism(0,400)<700,0>[A\otimes T^2B`T(A\otimes TB);\tau_{A,TB}]
    \morphism(700,400)<700,0>[T(A\otimes TB)`T^2(A\otimes B);T\tau_{A,B}]
  \efig
  \end{mathpar}
\end{definition}
  \label{lem:strong-monad}
  The monad on the SMCC in a SMCC-Lambek model is strong.
  Let $F:\cat{C}\vdash\cat{L}:G$ be a SMCC-Lambek model, where
  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is an SMCC,
  $(\cat{M},\otimes',I',\alpha',\lambda',\rho')$ is a Lambek category, and $(F,\m{})$ and
  $(G,\n{})$ are monoidal functors. Let $(T,\eta,\mu)$ be the monad on $\cat{C}$ where
  $T=GF$. We have proved that $T$ is monoidal with the natural transformation
  $\q{A,B}:TA\otimes TB\rightarrow T(A\otimes B)$ and the morphism $\q{I}:I\rightarrow TI$
  defined as in Lemma~\ref{lem:monoidal-monad}. \\
  We define the tensorial strength $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ as
  $\tau_{A,B}=\q{A,B}\circ\eta_A\otimes id_{TB}$. \\
  Since $\eta$ is a monoidal natural transformation, we have $\eta_I=G\m{I}\circ\n{I'}$.
  Therefore $\eta_I=\q{I}$. Thus the following diagram commutes because $T$ is monoidal,
  where the composition $\q{I,A}\circ\q{I}\otimes id_{TA}$ is the definition of $\tau_{I,A}$. So
  the first triangle in Defition~\ref{def:strong-monad} commutes.
    \square/->`->`->`<-/<600,400>[
      I\otimes TA`TI\otimes TA`TA`T(I\otimes A);
      \q{I}\otimes id_{TA}`\lambda_{TA}`\q{I,A}`T\lambda_A]
  Similarly, by using the definition of $\tau$, the the second triangle in the definition is
  equivalent to the following diagram, which commutes because $\eta$ is a monoidal natural
  transformation:
    \square/->`->`->`<-/<600,400>[
      A\otimes B`A\otimes TB`T(A\otimes B)`TA\otimes TB;
      id_A\otimes\eta_B`\eta_{A\otimes B}`\eta_A\otimes id_{TB}`\q{A,B}]
    \morphism(0,400)|m|<600,-400>[A\otimes B`TA\otimes TB;\eta_A\otimes\eta_B]
  The first pentagon in the definition commutes by the following diagram chasing, because
  $\eta$ are $\alpha$ natural transformations and $T$ is monoidal:
    \qtriangle|amm|/->`->`<-/<1000,400>[
      (A\otimes B)\otimes TC`T(A\otimes B)\otimes TC`(TA\otimes TB)\otimes TC;
      \eta_{A\otimes B}\otimes id_{TC}`
      (\eta_A\otimes\eta_B)\otimes id_{TC}`
      \q{A,B}\otimes id_{TC}]
    \morphism(0,400)<0,-400>[(A\otimes B)\otimes TC`A\otimes(B\otimes TC);\alpha_{A,B,TC}]
    \morphism(1000,0)|m|<0,-400>[
      (TA\otimes TB)\otimes TC`TA\otimes(TB\otimes TC);\alpha_{TA,TB,TC}]
    \Dtriangle(0,-800)|lmm|/->`->`<-/<1000,400>[
      A\otimes(B\otimes TC)`TA\otimes(TB\otimes TC)`A\otimes(TB\otimes TC);
      id_A\otimes(\eta_B\otimes id_{TC})`
      \eta_A\otimes(\eta_B\otimes id_{TC})`
      \eta_A\otimes id_{TB\otimes TC}]
    \morphism(0,-800)|b|<1000,0>[
      A\otimes(TB\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\q{B,C}]
    \qtriangle(1000,0)|amr|/->``->/<1000,400>[
      \q{A\otimes B,C}``T\alpha_{A,B,C}]
    \morphism(2000,-800)<0,800>[
      TA\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\q{A,B\otimes C}]
    \btriangle(1000,-800)|mmb|/`->`->/<1000,400>[
      TA\otimes(TB\otimes TC)`A\otimes T(B\otimes C)`TA\otimes T(B\otimes C);
      `id_{TA}\otimes\q{B,C}`\eta_A\otimes id_{T(B\otimes C)}]
  The last diagram in the definition commtues by the following diagram chasing, because $T$ is a
  monad, $\q{}$ is a natural transformation, and $\mu$ is a monoidal natural transformation:
    \ptriangle/->`->`/<700,400>[
      A\otimes T^2B`TA\otimes T^2B`A\otimes TB;\eta_A\otimes id_{T^2B}`id_A\otimes\mu_B`]
    \btriangle(0,-400)/->``->/<700,400>[
      A\otimes TB`TA\otimes TB`T(A\otimes B);\eta_A\otimes id_{TB}``\q{A,B}]
    \morphism(700,400)|m|<-700,-800>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
    \morphism(700,0)|m|<-700,-400>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
    \qtriangle(700,0)/->``->/<1800,400>[
      TA\otimes T^2B`T(A\otimes TB)`T(TA\otimes TB);\q{A,TB}``T(\eta_A\otimes id_{TB})]
    \btriangle(700,0)|mmm|/=`->`<-/<900,400>[
      TA\otimes T^2B`TA\otimes T^2B`T^2A\otimes T^2B;
      `T\eta_A\otimes id_{T^2B}`\mu_A\otimes id_{T^2B}]
    \morphism(1600,0)|m|<900,0>[T^2A\otimes T^2B`T(TA\otimes TB);\q{TA,TB}]
    \morphism(1600,0)|m|<-1600,-400>[T^2A\otimes T^2B`TA\otimes TB;\mu_A\otimes\mu_B]
    \dtriangle(700,-400)/`->`<-/<1800,400>[
      T(TA\otimes TB)`T(A\otimes B)`T^2(A\otimes B);`T\q{A,B}`\mu_{A\otimes B}]

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ be a symmetric monoidal category with exchange
  $\e{}$, and $(T,\eta,\mu)$ be a strong monad on $\cat{M}$. Then there is a \textbf{``twisted''
  tensorial strength} $\tau'_{A,B}:TA\otimes B\rightarrow T(A\otimes B)$ defined as
  $\tau'_{A,B}=T\e{}\circ\tau_{B,A}\circ\e{}$. We can construct a pair of natural
  transformations $\Phi$, $\Phi'$ with components
  $\Phi_{A,B},\Phi'_{A,B}:TA\otimes TB\rightarrow T(A\otimes B)$ defined as
  $\Phi_{A,B}=\mu_{A\otimes B}\circ T\tau'_{A,B}\circ\tau_{TA,B}$ and
  $\Phi'_{A,B}=\mu_{A\otimes B}\circ T\tau_{A,B}\circ\tau'_{A,TB}$. If $\Phi=\Phi'$, then the
  monad $T$ is \textbf{commutative}.
\end{definition}

\begin{lemma}
  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
  $T$ is a symmetric monoidal functor iff it is commutative.
\end{lemma}

\begin{theorem}
  The monad on the SMCC in a SMCC-Lambek model is not commutative.
\end{theorem}
